Evolution of solar wind discontinuities in the inner heliosphere

### 2024-11-04 article.qmd
update: new section on alignment effects and discontinuity properties

@@

- Normalized thickness and current density of discontinuities remain constant with radial distance. In contrast to @artemyevDynamicsIntenseCurrents2018 results that show a decrease  in normalized thickness and increase in normalized current density with radial distance.

>>>>

## The effect of alignment on discontinuity properties

![](figures/thickness_current.png)

![](figures/B_angle.png)

@@

- Normalized thickness and current density of discontinuities remain constant with radial distance (negligible change compared to their spread). In contrast to @artemyevDynamicsIntenseCurrents2018 results that show a decrease in normalized thickness and increase in normalized current density with radial distance.

- Better alignment period has a slightly better agreement of the properties of the discontinuities (normalized thickness, current density, $|\Delta \mathbf{B}/B|$ and rotation angle) between PSP and Earth-orbiting missions.
- $B_N/B$ and in-plane rotation angle are significantly different between PSP and Earth-orbiting missions independent of the alignment period.
